% -------------------------------------------------
% Narasimharao Bhavirisetty – Deloitte Data Engineer Resume
% -------------------------------------------------
\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{times}

% ----- Remove blue boxes & underlines from links -----
\hypersetup{
    colorlinks=false,
    pdfborder={0 0 0},
    hidelinks
}

% ----- Page layout -----
\geometry{a4paper, margin=0.75in}
\pagestyle{empty}

% ----- Section heading style -----
\titleformat{\section}{\Large\bfseries}{\thesection}{1em}{}
\titlespacing*{\section}{0pt}{10pt}{4pt}

% ----- Tighten itemize globally -----
\setlist[itemize]{topsep=1pt, partopsep=0pt, parsep=1pt, itemsep=1pt, leftmargin=*}

% ----- Compact project environment -----
\newenvironment{project}[2]
  {\par\textbf{#1}\hfill\textit{#2}\vspace{1pt}\begin{itemize}}
  {\end{itemize}\vspace{2pt}}

\begin{document}

% ==================== HEADER ====================
\begin{center}
  {\huge\textbf{Narasimharao Bhavirisetty}}\\[3pt]
  Data Engineer \textbullet{} Backend \& Data Pipeline Engineering \\[3pt]
  Narasaraopet, Andhra Pradesh, India \textbullet{} +91 63032 27485 \textbullet{} narasimharao2743@gmail.com \textbullet{} linkedin.com/in/narasimharao-bhavirisetty-0526891b0
\end{center}

\vspace{6pt}

% ==================== PROFESSIONAL SUMMARY ====================
\section*{Professional Summary}
\vspace{1pt}\hrule\vspace{4pt}
Data Engineer with 1.6+ years of hands-on experience building scalable data pipelines, automating workflows, and delivering analytics-driven solutions. Proficient in Python, SQL, and stream processing technologies including Kafka and PyFlink, with proven experience processing 50K+ events/day through multi-stage pipelines into columnar data stores. Experienced in data preprocessing, KPI reporting, and building ML models using Scikit-learn, Pandas, and NumPy. Comfortable working across the full data lifecycle: ingestion, transformation, analysis, and reporting, with a strong focus on data quality, automation, and measurable business outcomes.

% ==================== TECHNICAL SKILLS ====================
\section*{Technical Skills}
\vspace{1pt}\hrule\vspace{4pt}
\begin{itemize}
  \item \textbf{Languages}: Python, Java, SQL, PL/SQL
  \item \textbf{Data Engineering}: Kafka, Redpanda, PyFlink, Event-Driven Architecture, Data Pipelines, ETL/ELT Workflows
  \item \textbf{Databases \& Warehouses}: MySQL, MSSQL, ClickHouse, Redis
  \item \textbf{Big Data \& Cloud}: AWS, Spark, Snowflake, Databricks
  \item \textbf{Data Science \& ML}: Scikit-learn, Pandas, NumPy, EDA, Predictive Modelling, Statistical Analysis
  \item \textbf{Tools}: Jupyter Notebooks, Git, Docker, Postman, VS Code
  \item \textbf{Concepts}: OOP, Agile/Scrum, SDLC, Unit Testing, Data Quality, Technical Documentation, Clean Code
  \item \textbf{Frameworks}: Flask, FastAPI, Microservices
\end{itemize}

% ==================== PROFESSIONAL EXPERIENCE ====================
\section*{Professional Experience}
\vspace{1pt}\hrule\vspace{4pt}

\textbf{Software Engineer --- Data \& Pipeline Engineering} \hfill \textbf{Spizen Technologies (CLR3 Ventures), Bangalore} \\
\textit{December 2025 -- Present}
\begin{itemize}
  \item Designed and owned an end-to-end data pipeline processing 50K+ trade events/day through a multi-stage Kafka $\rightarrow$ PyFlink $\rightarrow$ ClickHouse $\rightarrow$ Redis architecture, enabling real-time analytics on token lifecycle events.
  \item Built fault-tolerant PyFlink streaming jobs with tumbling-window aggregations and checkpointing, reducing duplicate event records by $\sim$95\% and ensuring downstream data integrity.
  \item Engineered a behavioral classification system using Python and pattern analysis to detect anomalous trading activity, improving data signal quality and reliability for analytics consumers.
  \item Designed a real-time composite scoring engine that fuses multi-dimensional metrics from live event streams, emitting sub-second actionable signals for data-driven decision-making.
  \item Maintained technical documentation for data architecture, pipeline components, and schema interfaces to ensure reproducibility and team knowledge continuity.
\end{itemize}

\newpage
\textbf{Software Engineer --- Data \& Automation} \hfill \textbf{Algonox Technologies Pvt Ltd, Hyderabad} \\
\textit{September 2024 -- December 2025}
\begin{itemize}
  \item Boosted document data extraction accuracy by 40\% by designing multi-layered business rule validation to clean, reconcile, and preprocess noisy unstructured data at scale.
  \item Built an automated data workflow and email notification system for file queue transitions and SLA failure alerts, reducing manual monitoring overhead and improving response time.
  \item Developed an automated KPI reporting module tracking extraction accuracy and manual intervention rates, enabling data-driven performance reviews and a 20\% reduction in manual QA effort.
  \item Implemented a User Dormancy Management Module with scheduled tasks to enforce role-based lifecycle state transitions on configurable inactivity thresholds, strengthening data access governance and security compliance.
  \item Participated actively in Agile/Scrum ceremonies; contributed to code reviews and maintained clean, well-documented Python codebases.
\end{itemize}

% ==================== PERSONAL PROJECTS ====================
\section*{Personal Projects}
\vspace{1pt}\hrule\vspace{4pt}

\begin{project}{Airline Ticket Price Prediction --- ML Regression Pipeline}{Python, Scikit-learn, Pandas, NumPy, Jupyter Notebooks}
  \item Collected and preprocessed structured travel data, performing exploratory data analysis (EDA) to identify pricing trends, outliers, and key feature correlations.
  \item Built and validated a regression-based predictive model using cross-validation and hyperparameter tuning, achieving low Mean Absolute Error (MAE) on unseen test data.
  \item Generated visualizations (charts, correlation heatmaps) to communicate data insights and model findings to both technical and non-technical audiences.
\end{project}

% ==================== EDUCATION ====================
\section*{Education}
\vspace{1pt}\hrule\vspace{4pt}
\textbf{Bachelor of Technology in Computer Science} \hfill \textbf{Tirumala Engineering College, Narasaraopet} \\
\textit{January 2021 -- May 2024} \quad CGPA: 7.86 / 10 \quad Percentage: 74.67\%

\textbf{Intermediate (MPC)} \hfill \textbf{Bhavana Junior College, Narasaraopet} \\
\textit{June 2018 -- March 2020} \quad CGPA: 9.46 / 10

\textbf{Secondary School Certificate} \hfill \textbf{Sindhu High School, Narasaraopet} \\
\textit{June 2017 -- March 2018} \quad CGPA: 10.0 / 10

\vspace{6pt}

% ==================== CERTIFICATIONS ====================
\section*{Certifications}
\vspace{1pt}\hrule\vspace{4pt}
\begin{itemize}
  \item Microsoft Certified: Azure AI Fundamentals (Cert No: I664-7515, March 2023)
  \item Cloud Computing - NPTEL (IIT-backed national certification)
  \item AI and Machine Learning - Amazon Web Services (AWS)
\end{itemize}

% ==================== INTERESTS ====================
\section*{Interests}
\vspace{1pt}\hrule\vspace{4pt}
\begin{itemize}
  \item Data Engineering, Pipeline Architecture \& Scalable Systems
  \item AI, Machine Learning \& Large Language Models (LLMs)
  \item Problem Solving \& Automation
\end{itemize}

\end{document}
