% -------------------------------------------------
% Narasimharao Bhavirisetty – Sarvam AI Resume
% -------------------------------------------------
\documentclass[10pt]{article}
\AtBeginDocument{\fontsize{10.5}{13}\selectfont}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{times}

% ----- Remove blue boxes & underlines from links -----
\hypersetup{
    colorlinks=false,
    pdfborder={0 0 0},
    hidelinks
}

% ----- Page layout -----
\geometry{a4paper, top=0.45in, bottom=0.45in, left=0.65in, right=0.65in}
\pagestyle{empty}

% ----- Section heading style -----
\titleformat{\section}{\Large\bfseries}{\thesection}{1em}{}
\titlespacing*{\section}{0pt}{6pt}{2pt}

% ----- Tighten itemize globally -----
\setlist[itemize]{topsep=0pt, partopsep=0pt, parsep=0pt, itemsep=0pt, leftmargin=*}

\begin{document}

% ==================== HEADER ====================
\begin{center}
  {\huge\textbf{Narasimharao Bhavirisetty}}\\[3pt]
  Software Engineer \textbullet{} Backend \& API Systems \\[3pt]
  Bangalore, India \textbullet{} +91 63032 27485 \textbullet{} narasimharao2743@gmail.com \textbullet{} https://linkedin.com/in/narasimharao-bhavirisetty-0526891b0
\end{center}

\vspace{4pt}

% ==================== PROFESSIONAL SUMMARY ====================
\section*{Professional Summary}
\vspace{1pt}\hrule\vspace{4pt}
Backend Engineer with 1.7+ years of experience designing and building low-latency, fault-tolerant, event-driven API systems in Python. Hands-on expertise with Flask, Apache Kafka, Redis, ClickHouse, and PostgreSQL — the exact stack powering high-performance ML model serving infrastructure. Built real-time data pipelines processing 50K+ events daily with millisecond-level latency at Spizen Technologies, and scalable microservices with REST APIs at Algonox. Experienced with Docker, Kubernetes, gRPC, WebSockets, and CI/CD pipelines across distributed, cloud-agnostic environments.

% ==================== TECHNICAL SKILLS ====================
\section*{Technical Skills}
\vspace{1pt}\hrule\vspace{4pt}
\begin{itemize}
  \item \textbf{Languages}: Python, Java
  \item \textbf{API \& Protocols}: REST APIs, gRPC, WebSockets, HTTP, Flask
  \item \textbf{Databases}: PostgreSQL, Redis, ClickHouse, MySQL, MSSQL
  \item \textbf{Streaming \& Messaging}: Apache Kafka, Redis Streams, Redpanda, PyFlink
  \item \textbf{DevOps \& Infrastructure}: Docker, Kubernetes, CI/CD Pipelines, Git, Linux
  \item \textbf{Cloud}: AWS (Basics)
  \item \textbf{Concepts}: Distributed Systems, Microservices, Event-Driven Architecture, Low-Latency Systems, OOP, Agile, SDLC
\end{itemize}

% ==================== PROFESSIONAL EXPERIENCE ====================
\section*{Professional Experience}
\vspace{1pt}\hrule\vspace{4pt}

\textbf{Software Engineer} \hfill \textit{December 2025 -- Present} \\
\textbf{Spizen Technologies (CLR3 Ventures), Bangalore, India}
\begin{itemize}
  \item Designed and built a low-latency, fault-tolerant real-time API pipeline processing 50K+ trade events per day through Kafka, PyFlink, ClickHouse, and Redis, with millisecond-level response times for live investment signals.
  \item Engineered fault-tolerant stream processing jobs with tumbling window aggregations and checkpointing to deduplicate high-velocity events with 95\% accuracy across distributed Kafka topics.
  \item Built a real-time composite scoring engine exposing REST API endpoints that evaluate every trade event using multiple quality signals, emitting live investment signals within milliseconds.
  \item Developed a behavioral classification system to detect suspicious trading patterns via event-driven pipelines, improving platform integrity and downstream signal quality.
\end{itemize}

\textbf{Software Engineer} \hfill \textit{September 2024 -- December 2025} \\
\textbf{Algonox Technologies Pvt Ltd, Hyderabad, India}
\begin{itemize}
  \item Boosted data extraction accuracy by 40\% by implementing multi-layered validation microservices in Python with REST APIs to clean and reconcile noisy unstructured data at scale.
  \item Built a Flask-based email notification microservice with secure REST API endpoints for queue transitions and SLA alerts, deployed via Docker and integrated into CI/CD pipelines.
  \item Developed an automated KPI reporting service tracking accuracy metrics and intervention rates, enabling a 20\% reduction in manual QA effort through data-driven insights.
  \item Engineered a scheduled user lifecycle management module enforcing access control policies with authentication and authorisation checks, improving security compliance across the platform.
\end{itemize}

% ==================== EDUCATION ====================
\section*{Education}
\vspace{1pt}\hrule\vspace{4pt}
\textbf{B.Tech in Computer Science} \hfill \textbf{Tirumala Engineering College, Narasaraopet} \\
\textit{2021 -- 2024} \quad CGPA: 7.86 / 10

% ==================== CERTIFICATIONS ====================
\section*{Certifications}
\vspace{1pt}\hrule\vspace{4pt}
\begin{itemize}
  \item Cloud Computing -- NPTEL (IIT-backed national certification)
  \item AI and Machine Learning -- Amazon Web Services (AWS)
\end{itemize}

\end{document}
