% -------------------------------------------------
% Narasimharao Bhavirisetty – Deloitte Cover Letter
% -------------------------------------------------
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{times}

\hypersetup{
    colorlinks=false,
    pdfborder={0 0 0},
    hidelinks
}

\geometry{a4paper, top=0.75in, bottom=0.75in, left=0.85in, right=0.85in}
\pagestyle{empty}

\begin{document}

% ==================== HEADER ====================
\begin{flushleft}
{\large\textbf{Narasimharao Bhavirisetty}}\\
Bangalore, India\\
+91 63032 27485\\
narasimharao2743@gmail.com\\
linkedin.com/in/narasimharao-bhavirisetty-0526891b0
\end{flushleft}

\vspace{6pt}

\begin{flushleft}
\today\\[6pt]
Recruitment Team\\
Deloitte India (Offices of the US)\\
USI Tax - Data Engineering Division
\end{flushleft}

\vspace{6pt}

\textbf{Re: Application for Consultant - Data Engineer | Requisition Code: 330213}

\vspace{10pt}

Dear Hiring Team,

I am writing to express my strong interest in the Consultant - Data Engineer position at Deloitte USI Tax. Having been referred by a Deloitte colleague, I am excited about the opportunity to contribute to Deloitte's data engineering and tax technology initiatives, and I believe my background aligns well with what your team is looking for.

I am a Software Engineer with 1.6+ years of hands-on experience designing, building, and maintaining data pipelines and automation systems. In my current role at Spizen Technologies, I built an end-to-end real-time data pipeline processing over 50,000 events per day using Python, Kafka, PyFlink, ClickHouse, and Redis. I also developed automated classification and scoring systems that process live data streams and generate actionable insights within milliseconds. These experiences have given me a strong foundation in data engineering, stream processing, and building systems that handle large volumes of structured and unstructured data.

At Algonox Technologies, I improved document data extraction accuracy by 40\% through multi-layered data validation and preprocessing, built an automated KPI reporting module that reduced manual QA effort by 20\%, and developed workflow automation systems to enhance operational efficiency and compliance. This work directly maps to Deloitte's requirement for professionals who can collect, clean, preprocess data, support data pipelines, and generate reports for both technical and non-technical stakeholders.

I have practical experience with Python, SQL, Pandas, NumPy, Scikit-learn, and Jupyter Notebooks for data analysis and predictive modelling. I am also Microsoft Certified in Azure AI Fundamentals and hold certifications in Cloud Computing (NPTEL) and AI and Machine Learning (AWS), which reflect my commitment to staying current with modern data and cloud technologies. I am aware of big data technologies including Snowflake, Databricks, and Spark, and I am eager to deepen this expertise within Deloitte's environment.

What excites me most about this role is the opportunity to apply data engineering skills in the tax technology domain - an area where accuracy, automation, and data quality directly impact client outcomes. I am a fast learner who is comfortable working with minimal supervision, collaborating across cross-functional teams, and presenting findings clearly to both technical and business audiences.

I am confident that my experience in data pipelines, automation, and analytics, combined with my drive to learn and deliver impact, make me a strong fit for this role. I would welcome the opportunity to discuss how I can contribute to Deloitte's mission of making an impact that matters.

Thank you for your time and consideration.

\vspace{16pt}

Sincerely,\\[4pt]
\textbf{Narasimharao Bhavirisetty}

\end{document}
