% -------------------------------------------------
% Narasimharao Bhavirisetty – GenAI Resume
% -------------------------------------------------
\documentclass[10pt]{article}
\AtBeginDocument{\fontsize{10.5}{13}\selectfont}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{times}

% ----- Remove blue boxes & underlines from links -----
\hypersetup{
    colorlinks=false,
    pdfborder={0 0 0},
    hidelinks
}

% ----- Page layout -----
\geometry{a4paper, top=0.5in, bottom=0.5in, left=0.65in, right=0.65in}
\pagestyle{empty}

% ----- Section heading style -----
\titleformat{\section}{\Large\bfseries}{\thesection}{1em}{}
\titlespacing*{\section}{0pt}{6pt}{2pt}

% ----- Tighten itemize globally -----
\setlist[itemize]{topsep=0pt, partopsep=0pt, parsep=0pt, itemsep=0pt, leftmargin=*}

\begin{document}

% ==================== HEADER ====================
\begin{center}
  {\huge\textbf{Narasimharao Bhavirisetty}}\\[3pt]
  Software Engineer \textbullet{} Backend, Data Engineering \& GenAI \\[3pt]
  Bangalore, India \textbullet{} +91 63032 27485 \textbullet{} narasimharao2743@gmail.com \textbullet{} https://linkedin.com/in/narasimharao-bhavirisetty-0526891b0
\end{center}

\vspace{6pt}

% ==================== PROFESSIONAL SUMMARY ====================
\section*{Professional Summary}
\vspace{1pt}\hrule\vspace{4pt}
Software Engineer with 1.5+ years of experience designing and delivering event-driven backend systems and real-time data pipelines at scale. Specialized in Python and Apache Kafka-based stream processing, with proven results processing 50K+ trade events daily through ClickHouse and Redis with millisecond-level latency. Demonstrated impact at Algonox with a 40\% improvement in data extraction accuracy through validation-driven automation. Complementing this foundation with hands-on expertise in GenAI — including RAG pipelines, vector search, model inferencing, and prompt engineering — positioned to contribute across both enterprise data infrastructure and AI-driven application layers.

% ==================== TECHNICAL SKILLS ====================
\section*{Technical Skills}
\vspace{1pt}\hrule\vspace{4pt}
\begin{itemize}
  \item \textbf{GenAI}: RAG, Vector Search, Model Inferencing, Prompt Engineering
  \item \textbf{Languages}: Python, Java
  \item \textbf{Databases}: MySQL, MSSQL, PostgreSQL, ClickHouse, Redis
  \item \textbf{Stream Processing}: Apache Kafka, Redpanda, PyFlink
  \item \textbf{Frameworks \& Tools}: Flask, Docker, Kubernetes, Git, Postman, Linux
  \item \textbf{Concepts}: REST APIs, Microservices, Distributed Systems, Event-Driven Architecture, OOP, Agile, SDLC
\end{itemize}

% ==================== PROFESSIONAL EXPERIENCE ====================
\section*{Professional Experience}
\vspace{1pt}\hrule\vspace{4pt}

\textbf{Software Engineer} \hfill \textit{December 2025 -- Present} \\
\textbf{Spizen Technologies (CLR3 Ventures), Bangalore, India}
\begin{itemize}
  \item Designed and built a real-time data pipeline processing 50K+ trade events per day through Kafka, PyFlink, ClickHouse, and Redis, enabling live tracking and analytics on trading activity.
  \item Built reliable stream processing jobs that automatically detect and remove duplicate records with 95\% accuracy, ensuring clean data for all downstream analytics.
  \item Developed an automated classification system to identify suspicious trading patterns and bot activity, improving the quality of investment signals on the platform.
  \item Built a real-time scoring system that evaluates every trade event and generates live investment signals within milliseconds using multiple quality metrics.
\end{itemize}

\textbf{Software Engineer} \hfill \textit{September 2024 -- December 2025} \\
\textbf{Algonox Technologies Pvt Ltd, Hyderabad, India}
\begin{itemize}
  \item Boosted document data extraction accuracy by 40\% by implementing multi-layered business rule validation to clean and reconcile noisy, unstructured input data at scale.
  \item Built an automated email notification microservice for file queue transitions and SLA failure alerts, reducing manual monitoring overhead and improving response time.
  \item Developed an automated KPI reporting module tracking extraction accuracy and manual intervention rates, enabling data-driven reviews and a 20\% reduction in manual QA effort.
  \item Built a scheduled module to automatically manage user account states based on inactivity periods, ensuring only active users retain system access and improving security compliance.
\end{itemize}

% ==================== EDUCATION ====================
\section*{Education}
\vspace{1pt}\hrule\vspace{4pt}
\textbf{B.Tech in Computer Science} \hfill \textbf{Tirumala Engineering College, Narasaraopet} \\
\textit{2021 -- 2024} \quad CGPA: 7.86 / 10

\textbf{Intermediate (MPC)} \hfill \textbf{Bhavana Junior College, Narasaraopet} \\
\textit{2018 -- 2020} \quad CGPA: 9.46 / 10

\textbf{Secondary School Certificate (SSC)} \hfill \textbf{Sindhu High School, Narasaraopet} \\
\textit{2018} \quad CGPA: 10 / 10

% ==================== CERTIFICATIONS ====================
\section*{Certifications}
\vspace{1pt}\hrule\vspace{4pt}
\begin{itemize}
  \item AWS - AI and Machine Learning
\end{itemize}

\end{document}
