% -------------------------------------------------
% Narasimharao Bhavirisetty – Visa Software Engineer Resume
% -------------------------------------------------
\documentclass[10pt]{article}
\AtBeginDocument{\fontsize{10.5}{13}\selectfont}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{times}

% ----- Remove blue boxes & underlines from links -----
\hypersetup{
    colorlinks=false,
    pdfborder={0 0 0},
    hidelinks
}

% ----- Page layout -----
\geometry{a4paper, top=0.45in, bottom=0.45in, left=0.65in, right=0.65in}
\pagestyle{empty}

% ----- Section heading style -----
\titleformat{\section}{\Large\bfseries}{\thesection}{1em}{}
\titlespacing*{\section}{0pt}{6pt}{2pt}

% ----- Tighten itemize globally -----
\setlist[itemize]{topsep=0pt, partopsep=0pt, parsep=0pt, itemsep=0pt, leftmargin=*}

\begin{document}

% ==================== HEADER ====================
\begin{center}
  {\huge\textbf{Narasimharao Bhavirisetty}}\\[3pt]
  Software Engineer \textbullet{} Backend \& Distributed Systems \\[3pt]
  Bangalore, India \textbullet{} +91 63032 27485 \textbullet{} narasimharao2743@gmail.com \textbullet{} linkedin.com/in/narasimharao-bhavirisetty-0526891b0
\end{center}

\vspace{4pt}

% ==================== PROFESSIONAL SUMMARY ====================
\section*{Professional Summary}
\vspace{1pt}\hrule\vspace{4pt}
Software Engineer with 1.7+ years of experience building high-throughput, event-driven backend systems for real-time transaction processing. Specialized in Python and Java with deep hands-on expertise in Apache Kafka stream processing, processing 50K+ events daily with millisecond-level latency through distributed microservices. Experienced across the full SDLC in Agile teams — from system design and development to containerized deployment using Docker and Kubernetes. Proven ability to build fault-tolerant, scalable systems with strong attention to data integrity, security compliance, and production reliability.

% ==================== TECHNICAL SKILLS ====================
\section*{Technical Skills}
\vspace{1pt}\hrule\vspace{4pt}
\begin{itemize}
  \item \textbf{Languages}: Python, Java
  \item \textbf{Frameworks \& Libraries}: Flask, PyFlink, REST APIs
  \item \textbf{Databases}: MySQL, MSSQL, ClickHouse, Redis, PostgreSQL
  \item \textbf{Streaming \& Messaging}: Apache Kafka, Redpanda, Event-Driven Architecture
  \item \textbf{DevOps \& Infrastructure}: Docker, Kubernetes, CI/CD Pipelines, Git, GitHub Actions
  \item \textbf{Concepts}: Distributed Systems, Microservices, OOP, System Design, Agile/Scrum, SDLC
\end{itemize}

% ==================== PROFESSIONAL EXPERIENCE ====================
\section*{Professional Experience}
\vspace{1pt}\hrule\vspace{4pt}

\textbf{Software Engineer} \hfill \textbf{Spizen Technologies (CLR3 Ventures), Bangalore, India} \\
\textit{December 2025 -- Present}
\begin{itemize}
  \item Designed and built a high-throughput real-time transaction pipeline processing 50K+ events per day through Kafka, PyFlink, ClickHouse, and Redis with millisecond-level latency, enabling live tracking and analytics.
  \item Engineered fault-tolerant stream processing jobs with tumbling window aggregations and checkpointing to detect and eliminate duplicate records with 95\% accuracy across distributed Kafka topics.
  \item Developed an automated behavioral classification system to identify suspicious high-frequency trading patterns, improving signal quality and platform integrity — directly analogous to payment fraud detection.
  \item Built a real-time composite scoring engine that evaluates every transaction event using multiple quality metrics and emits live signals within milliseconds, deployed via Docker on Kubernetes.
\end{itemize}

\textbf{Software Engineer} \hfill \textbf{Algonox Technologies Pvt Ltd, Hyderabad, India} \\
\textit{September 2024 -- December 2025}
\begin{itemize}
  \item Boosted data extraction accuracy by 40\% by implementing multi-layered business rule validation in Python to clean and reconcile noisy, unstructured data at scale within a microservices architecture.
  \item Built a REST API-based email notification microservice for queue transitions and SLA failure alerts, integrated via CI/CD pipelines (GitHub Actions) and reducing manual monitoring overhead.
  \item Developed an automated KPI reporting module tracking accuracy and intervention rates, enabling data-driven decisions and a 20\% reduction in manual QA effort.
  \item Built a scheduled security module to manage user account lifecycle states based on inactivity thresholds, enforcing access control and improving compliance across the platform.
\end{itemize}

% ==================== EDUCATION ====================
\section*{Education}
\vspace{1pt}\hrule\vspace{4pt}
\textbf{B.Tech in Computer Science} \hfill \textbf{Tirumala Engineering College, Narasaraopet} \\
\textit{2021 -- 2024} \quad CGPA: 7.86 / 10

% ==================== CERTIFICATIONS ====================
\section*{Certifications}
\vspace{1pt}\hrule\vspace{4pt}
\begin{itemize}
  \item Cloud Computing -- NPTEL (IIT-backed national certification)
  \item AI and Machine Learning -- Amazon Web Services (AWS)
\end{itemize}

% ==================== PROJECTS ====================
\section*{Key Project}
\vspace{1pt}\hrule\vspace{4pt}
\textbf{Airline Ticket Price Prediction} \hfill \textit{Python, Scikit-learn, Pandas, NumPy} \\
Built a regression-based ML model to forecast ticket prices; performed feature engineering and model evaluation achieving low MAE, with insights presented for strategic decision-making.

\end{document}
