% -------------------------------------------------
% Narasimharao Bhavirisetty – Accenture Resume
% -------------------------------------------------
\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{times}

% ----- Remove blue boxes & underlines from links -----
\hypersetup{
    colorlinks=false,
    pdfborder={0 0 0},
    hidelinks
}

% ----- Page layout -----
\geometry{a4paper, margin=0.75in}
\pagestyle{empty}

% ----- Section heading style -----
\titleformat{\section}{\Large\bfseries}{\thesection}{1em}{}
\titlespacing*{\section}{0pt}{10pt}{4pt}

% ----- Tighten itemize globally -----
\setlist[itemize]{topsep=1pt, partopsep=0pt, parsep=1pt, itemsep=1pt, leftmargin=*}

% ----- Compact project environment -----
\newenvironment{project}[1]
  {\par\textbf{#1}\hfill\textit{Python, Scikit-learn, Pandas, NumPy}\vspace{1pt}\begin{itemize}}
  {\end{itemize}\vspace{2pt}}

\begin{document}

% ==================== HEADER ====================
\begin{center}
  {\huge\textbf{Narasimharao Bhavirisetty}}\\[3pt]
  Narasaraopet, Andhra Pradesh, India \\[1pt]
  +91 63032 27485 \textbullet{} narasimharao2743@gmail.com \textbullet{}
  linkedin.com/in/narasimharao-bhavirisetty-0526891b0
\end{center}

\vspace{6pt}

% ==================== PROFESSIONAL SUMMARY ====================
\section*{Professional Summary}
\vspace{1pt}\hrule\vspace{4pt}
Results-driven Python Developer with 1.5+ years of experience building real-time data pipelines, event-driven systems, and backend automation using object-oriented programming principles. Proficient in Python, Kafka, ClickHouse, Redis, PyFlink, and REST APIs. Experienced in agile development practices, stream processing, and machine learning workflows. Solid knowledge of SDLC, debugging, clean code practices, and production support.

% ==================== SKILLS ====================
\section*{Skills}
\vspace{1pt}\hrule\vspace{4pt}
\begin{itemize}
  \item \textbf{Languages}: Python, Java
  \item \textbf{Frameworks}: Flask, PyFlink
  \item \textbf{Databases}: MySQL, MSSQL, ClickHouse, Redis
  \item \textbf{Concepts}: OOP, Agile, SDLC, REST API Design, Debugging, Production Issue Analysis, Version Control (Git), Code Reviews, Clean Code Practices
  \item \textbf{Libraries}: NumPy, Pandas, Scikit-learn
  \item \textbf{Tools}: Git, Postman, VS Code
  \item \textbf{Other Skills}: Data Cleaning, Automation, Machine Learning Algorithms, Stream Processing
  \item \textbf{Event Streaming}: Kafka, Redpanda
  \item \textbf{Blockchain}: Solana, Pump.fun, Protobuf
  \item \textbf{Cloud}: AWS Basics
\end{itemize}

% ==================== PROFESSIONAL EXPERIENCE ====================
\section*{Professional Experience}
\vspace{1pt}\hrule\vspace{4pt}

\textbf{Software Engineer} \hfill \textbf{Spizen Technologies (CLR3 Ventures), Bangalore, India} \\
\textit{December 2025 -- Current}
\begin{itemize}
  \item Built an end-to-end real-time data pipeline with multiple streaming jobs processing blockchain trade and lifecycle events through Kafka, ClickHouse, and Redis, tracking full token lifecycle from creation to graduation.
  \item Designed PyFlink streaming jobs with tumbling window aggregations to deduplicate high-velocity event data across Kafka topics with fault-tolerant checkpointing.
  \item Built a behavioral classification system using object-oriented design and pattern analysis to detect anomalous activity, improving data quality and signal reliability.
  \item Engineered a real-time composite scoring engine that processes live event streams, incorporating multi-dimensional quality signals to emit actionable outputs with low latency.
\end{itemize}

\textbf{Software Engineer} \hfill \textbf{Algonox Technologies Pvt Ltd, Hyderabad, India} \\
\textit{September 2024 -- December 2025}
\begin{itemize}
  \item Built automated email notification system for file queue transitions and failure alerts, improving SLA compliance.
  \item Implemented complex business rules to clean and validate noisy data, boosting data extraction accuracy by 40\%.
  \item Designed automated KPI reporting system to track extraction accuracy and manual intervention rates, enabling data-driven performance improvements.
  \item Developed User Dormancy Management Module with scheduled tasks to manage user lifecycle states based on inactivity thresholds, enhancing security and access control.
  \item Participated in agile development cycles, contributed to code reviews, and maintained clean, well-documented Python codebases to ensure long-term maintainability.
\end{itemize}

% ==================== EDUCATION ====================
\section*{Education}
\vspace{1pt}\hrule\vspace{4pt}
\textbf{Bachelor of Technology in Computer Science} \hfill \textbf{Tirumala Engineering College, Narasaraopet} \\
\textit{January 2021 -- May 2024} \quad SGPA: 7.86 | Percentage: 74.67\%

\textbf{Intermediate (MPC)} \hfill \textbf{Bhavana Junior College, Narasaraopet} \\
\textit{June 2018 -- March 2020}

\textbf{Secondary School Certificate} \hfill \textbf{Sindhu High School, Narasaraopet} \\
\textit{June 2017 -- March 2018}

\vspace{6pt}

% ==================== PERSONAL PROJECTS ====================
\section*{Personal Projects}
\vspace{1pt}\hrule\vspace{4pt}
\begin{project}{Predicting Airline Ticket Prices Using Machine Learning}
  \item Built a regression-based model using Scikit-learn to forecast airline ticket prices based on travel data.
  \item Performed data preprocessing, feature engineering, and model evaluation, achieving low Mean Absolute Error (MAE).
  \item Presented key pricing insights and visualizations to guide strategic decisions.
\end{project}

% ==================== CERTIFICATIONS ====================
\section*{Certifications}
\vspace{1pt}\hrule\vspace{4pt}
\begin{itemize}
  \item Cloud Computing, NPTEL
  \item AI and Machine Learning, Amazon Web Services (AWS)
\end{itemize}

% ==================== INTERESTS ====================
\section*{Interests}
\vspace{1pt}\hrule\vspace{4pt}
\begin{itemize}
  \item Problem Solving \& Automation
  \item Economics, Business \& Finance
  \item AI Innovations \& Tech Trends
\end{itemize}

\end{document}
