% -------------------------------------------------
% Narasimharao Bhavirisetty – Raphus Solutions Cover Letter
% -------------------------------------------------
\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{times}

\hypersetup{
    colorlinks=false,
    pdfborder={0 0 0},
    hidelinks
}

\geometry{a4paper, top=0.75in, bottom=0.75in, left=0.85in, right=0.85in}
\pagestyle{empty}

\begin{document}

% ==================== HEADER ====================
\begin{flushleft}
{\Large\textbf{Narasimharao Bhavirisetty}}\\[3pt]
Software Engineer \textbar{} Backend Developer\\[3pt]
Bangalore, India \textbullet{} +91 63032 27485 \textbullet{} narasimharao2743@gmail.com\\
https://linkedin.com/in/narasimharao-bhavirisetty-0526891b0
\end{flushleft}

\vspace{12pt}

\begin{flushleft}
\textbf{To,}\\
The Hiring Team\\
Raphus Solutions\\
\end{flushleft}

\vspace{8pt}

\textbf{Subject: Application for Backend Developer Role}

\vspace{10pt}

Dear Hiring Team,

I am writing to express my interest in the Backend Developer role at Raphus Solutions. With 1.7+ years of hands-on experience building production-grade, event-driven backend systems, I am drawn to Raphus's mission of empowering enterprises through cutting-edge technologies like AI, Cloud, and Digital Process Automation --- areas that directly align with the work I have been doing and the direction I want to grow in.

In my current role at Spizen Technologies, I designed and built a real-time data pipeline processing 50K+ events daily using Python, Apache Kafka, PyFlink, ClickHouse, and Redis --- with millisecond-level latency and 95\% deduplication accuracy. At Algonox Technologies, I developed microservices-based automation systems that improved data extraction accuracy by 40\% and reduced manual QA effort by 20\%. These experiences have given me deep exposure to distributed systems, REST APIs, Docker, and Kubernetes --- the core building blocks of scalable digital transformation platforms.

What excites me about Raphus Solutions specifically is the breadth of disruptive technologies you work with --- AI, LLMs, Blockchain, Predictive Analytics, and Edge Computing. As a fast-growing company, Raphus offers the kind of environment where a backend engineer can contribute across multiple technology domains, move fast, and see direct impact. I thrive in exactly this kind of setup --- I am comfortable picking up new technologies quickly and building reliable systems under real-world constraints.

I am confident that my Python backend expertise, stream processing experience, and passion for building scalable systems make me a strong fit for your team. I would love the opportunity to contribute to Raphus's digital transformation journey.

Thank you for your time and consideration. I look forward to hearing from you.

\vspace{16pt}

\textbf{Warm regards,}\\[6pt]
\textbf{Narasimharao Bhavirisetty}\\
+91 63032 27485\\
narasimharao2743@gmail.com\\
https://linkedin.com/in/narasimharao-bhavirisetty-0526891b0

\end{document}
